---
title: "FC Cincinnati vs Tigres UANL"
format:
  html:
    theme: lumen
    css: ../styles.css
    toc: true
    toc-depth: 3
---

# Well that's a great start
This game started off in flying colors for the orange and blue, with a beautifully setup (Denkey) goal for none other than Pavel Bucha. It was a nice bit of play on the edge of the box between Yedlin with holdup play from Denkey who laid the ball of nicely for Bucha to nestle into the bottom corner in only the 3rd minute.

```{r setup, include=FALSE}
# Load required libraries
library(ggplot2)
library(grid)
library(ggforce)

# Define soccer field function
create_soccer_field <- function(point1_x = -44.5, point1_y = -10, 
                              point2_x = 15, point2_y = -20,
                              arrow_direction = "2to1",
                              player1_name = NULL,
                              player2_name = NULL,
                              point1_color = "#F05323",
                              point2_color = "#263B80") {
  # Create base plot with field dimensions
  p <- ggplot() +
    # Add field outline
    geom_rect(aes(xmin = -52.5, xmax = 52.5, ymin = -34, ymax = 34),
              fill = "darkgreen", color = "white") +
    # Add penalty areas
    geom_rect(aes(xmin = 35.3, xmax = 52.5, ymin = -20.9, ymax = 20.9),
              fill = "darkgreen", color = "white") +
    geom_rect(aes(xmin = -52.5, xmax = -35.3, ymin = -20.9, ymax = 20.9),
              fill = "darkgreen", color = "white") +
    # Add goals
    geom_rect(aes(xmin = 52.5, xmax = 53.5, ymin = -3.6, ymax = 3.6),
              fill = "white", color = "white") +
    geom_rect(aes(xmin = -53.5, xmax = -52.5, ymin = -3.6, ymax = 3.6),
              fill = "white", color = "white") +
    # Add center circle
    geom_circle(aes(x0 = 0, y0 = 0, r = 9.15), color = "white", fill = "darkgreen") +
    # Add center line
    geom_vline(xintercept = 0, color = "white") +
    # Add points and arrow
    geom_point(aes(x = point1_x, y = point1_y), color = point1_color, size = 4) +
    geom_point(aes(x = point2_x, y = point2_y), color = point2_color, size = 4)
    
  # Add arrow based on direction parameter
  if (arrow_direction == "1to2") {
    p <- p + geom_segment(aes(x = point1_x, y = point1_y,
                             xend = point2_x, yend = point2_y),
                         arrow = arrow(length = unit(0.5, "cm")),
                         color = "white", size = 1)
  } else if (arrow_direction == "2to1") {
    p <- p + geom_segment(aes(x = point2_x, y = point2_y,
                             xend = point1_x, yend = point1_y),
                         arrow = arrow(length = unit(0.5, "cm")),
                         color = "white", size = 1)
  }
  
  # Add player names if provided
  if (!is.null(player1_name)) {
    p <- p + annotate("text", x = point1_x, y = point1_y + 2,
                     label = player1_name, color = "white")
  }
  if (!is.null(player2_name)) {
    p <- p + annotate("text", x = point2_x, y = point2_y + 2,
                     label = player2_name, color = "white")
  }
  
  # Add theme elements
  p + theme_void() +
    theme(panel.background = element_rect(fill = "darkgreen"),
          plot.background = element_rect(fill = "darkgreen")) +
    coord_fixed(ratio = 1)
}
```

```{r first-goal, echo=FALSE, warning=FALSE, message=FALSE}
soccer_field_custom <- create_soccer_field(
    point1_x = 37, 
    point1_y = -3, 
    point2_x = 30, 
    point2_y = 4, 
    arrow_direction = "1to2", 
    player1_name = "Denkey",
    player2_name = "Bucha",
    point1_color = "orange",
    point2_color = "blue"
)
print(soccer_field_custom)
```

For the next 10-ish minutes, we looked really solid and were holding possession, which we were able to convert into some nice chances. However, in the 16th minute, Tigres leveled the game through a high, looping cross that came in from the byline and found the head of Nicolás Ibáñez, who rose over Hadebe to level the game at 1-1.

```{r second-goal, echo=FALSE, warning=FALSE, message=FALSE}
soccer_field_custom <- create_soccer_field(
    point1_x = -50, 
    point1_y = -22, 
    point2_x = -50, 
    point2_y = 4, 
    arrow_direction = "1to2", 
    player1_name = "Cordova",
    player2_name = "Ibanez",
    point1_color = "yellow",
    point2_color = "blue"
)
print(soccer_field_custom)
```

Then, only a few minutes later, through some very nice buildup from the midfield, FCC carved out a beautiful chance that fell to Denkey inside the box with a good amount of space. I couldn’t have wished for this chance to fall to anyone else on the pitch, but we missed the opportunity for a swift reply when Denkey put the ball wide.

Again, in the 35th minute, through some bad play at the back from Tigres, Denkey was through on goal once more. It wasn’t as great of a chance this time, and he was unable to convert. Tigres also had a nice chance in the 35th minute that was nicely dealt with by Celentano.

The rest of the game was cagey, with good chances from Evander on the edge of the box around the 60th minute and from Orellano, who finally returned to the squad with a solid 30-minute stint in the second half. Sadly, the game ended in a 1-1 draw, and Cincy will head into next week’s fixture in San Nicolás, Mexico.
#Thoughts + a bit of midfield analysis
First, here’s a graph to show the midfield breakdown for Evander vs Tigres.

```{r,echo = FALSE}
# Load necessary libraries
install.packages("ggplot2")
install.packages("tidyr")

library(ggplot2)
library(tidyr)

# Define FC Cincinnati colors
fc_orange <- "#F05323"
fc_blue <- "#003087"

# Create the dataframe
evander_stats <- data.frame(
  Metric = c("Shots", "Shots on Target", "Goals", "Assists", "Key Passes", "Dribbles"),
  Vs_Tigres = c(3, 1, 0, 0, 2, 4),
  Avg_2024 = c(3.18, 1.29, 0.30, 0.36, 2.74, 2.42)
)

# Reshape the dataframe for ggplot
evander_stats_long <- evander_stats %>%
  pivot_longer(cols = c(Vs_Tigres, Avg_2024), 
               names_to = "Type", 
               values_to = "Value")

# Define custom colors for each category
custom_colors <- c("Vs_Tigres" = fc_orange, "Avg_2024" = fc_blue)

# Plot the data using ggplot2 with dark theme
ggplot(evander_stats_long, aes(x = Metric, y = Value, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge", color = "white", width = 0.6) +
  geom_text(aes(label = round(Value, 2)), 
            position = position_dodge(width = 0.6), 
            vjust = -0.3, size = 5, color = "white") +
  scale_fill_manual(values = custom_colors, labels = c("Vs Tigres", "2024 Avg")) +
  theme_minimal(base_size = 14) +
  labs(title = "Evander's Performance vs Tigres UANL Compared to 2024 Season Average",
       x = "Metric",
       y = "Value",
       fill = "Performance") +
  theme(
    plot.background = element_rect(fill = "black", color = NA),
    panel.background = element_rect(fill = "black", color = NA),
    legend.background = element_rect(fill = "black", color = NA),
    legend.key = element_rect(fill = "black"),
    text = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    legend.text = element_text(color = "white"),
    legend.title = element_text(color = "white"),
    axis.text.x = element_text(angle = 30, hjust = 1),
    panel.grid = element_blank()
  )
```

I wanted to key in on Evander (who I hope is okay and should be after he took a hard hit from a TIGRES player), not because he played poorly, but simply because I think he is the key going forward. His ability to pull players in on the flanks, like spreading passes out to Yedlin for a cross, or his ability to find Denkey with a quick flick or backheel is immense, and I really hope we see more of that in the future. The quicker he and Denkey can click, the better this team can become. I also think the re-integration (Severance haha) of Orellano back into the side will help provide another quality option in the attack.

I compared his stats in this game to his average last season, not because it necessarily makes the most analytical sense to do so—because it does not—but because it shows his potential. If I am remembering correctly, he was second only to Messi in goal contributions last season. Now, combine that with Denkey’s ability + Orellano, and we can be a serious contender for any trophy.

That being said, to have a shot at continuing our push towards the CCL trophy, we have a tough assignment Tuesday in Mexico. It was always going to be difficult playing on the road in what will be a raucous environment, but with the away goal rule, it becomes even more of a hill to climb. However, we can do it. We will just have to play as a fluid, cohesive unit and take our chances when they come because we need goals and cannot afford to give any away.

#Final Thoughts + Toronto Predictions
I would love to see a huge win today, and even more to see Denkey get a goal (or more). I am going to predict a 3-1 FCC win with a Denkey brace and a wildcard Yedlin goal. As always, thanks for reading, and cheers! ALL FOR CINCY!